Fast and optimal centroiding of faint stars

### 2015-02-13 ms/figure.tex
Update figure.tex

\begin{abstract}
One of the most demanding tasks in astronomical image processing---in terms of precision---is the centroiding of stars. 
Upcoming large surveys are going to take images of billions of point sources, 
including many faint stars, with short exposure times. Real-time estimation of the
centroid of stars is crucial for real-time PSF estimation, and precision is required
for measurements of proper motion. In this work, we aim to compare the performance of
fast and slow centroiding methods, when they are applied
to relatively low signal-to-noise ratio stars in a wide range of psf sizes.
In order to investigate how information-preserving these techniques are, we compare
the root-mean-squared-error arising from these centroiding methods with the fundamental Cramer-Rao
lower bound. The methods we discuss in this paper include weighted moments, naive 3$\times$3 polynomial centroiding,
the 3$\times$3 quartic approximation used in the \textsl{Sloan Digital Sky Surveys}, and PSF profile fitting
(with both the correct and the incorrect PSF).
We recommend a particular form of polynomial cetroiding; it is very fast.
Although it is not as accurate as PSF profile fitting with a good PSF estimate,
it comes close to saturating the Cramer-Rao lower bound in a wide range of conditions.
\end{abstract}

>>>>

\begin{abstract}
One of the most demanding tasks in astronomical image processing---in terms of precision---is
the centroiding of stars. Upcoming large surveys are going to take images of billions of point sources, 
including many faint stars, with short exposure times. Real-time estimation of the
centroid of stars is crucial for real-time PSF estimation, and precision is required
for measurements of proper motion. In this work, we aim to compare the performance of
fast and slow centroiding methods, when they are applied
to relatively low signal-to-noise ratio stars in a wide range of psf sizes.
In order to investigate how information-preserving these techniques are, we compare
the root-mean-squared-error arising from these centroiding methods with the fundamental Cramer-Rao
lower bound.

%include weighted moments, naive 3$\times$3 polynomial centroiding,
%the 3$\times$3 quartic approximation used in the \textsl{Sloan Digital Sky Surveys}, and PSF profile fitting
%(with both the correct and the incorrect PSF).
%We recommend a particular form of polynomial cetroiding; it is very fast.
%Although it is not as accurate as PSF profile fitting with a good PSF estimate,
%it comes close to saturating the Cramer-Rao lower bound in a wide range of conditions.
\end{abstract}
